Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=6.5, fig.width=30, dpi=300}
mix_data_1 <- lapply(seq_along(sample_sizes), function(i) {
  n <- sample_sizes[i]
  norm_part <- norm_data[[i]][1:(k /2), 1:n]
  chisq_part <- matrix(rchisq(n *k /2, df =5), k /2)
  rbind(norm_part, chisq_part)
})

@@

```{r fig.height=6.5, fig.width=30, dpi=300}
mix_data_2 <- lapply(sample_sizes, function(n) {
  chisq_a <- matrix(rchisq(n*k/2, df = 3), k/2)
  chisq_b <- matrix(rchisq(n*k/2, df = 8), k/2)
  rbind(chisq_a, chisq_b)
})

@@

```{r fig.height=6.5, fig.width=30, dpi=300}
mix_data_3 <- lapply(seq_along(sample_sizes), function(i) {
  n <-  sample_sizes[i]
  chisq_a <- matrix(rchisq(n*k/4, df = 3), k/4)
  chisq_b <- matrix(rchisq(n*k/4, df = 8), k/4)
  norm_a <- norm_data[[i]][1:(k /4), 1:n]
  norm_b <- matrix(rnorm(n*k/4, mean = 2, sd = 1.5), k/4)
  rbind(chisq_a, chisq_b, norm_a, norm_b)
})

@@

>>>>

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
mix_data_1 <- lapply(seq_along(sample_sizes), function(i) {
  n <- sample_sizes[i]
  norm_part <- matrix(rnorm(n*k/2, mean = 0, sd = 1), k/2)
  chisq_part <- matrix(rchisq(n *k /2, df =5), k /2)
  rbind(norm_part, chisq_part)
})

@@

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
mix_data_2 <- lapply(sample_sizes, function(n) {
  chisq_a <- matrix(rchisq(n*k/2, df = 3), k/2)
  chisq_b <- matrix(rchisq(n*k/2, df = 8), k/2)
  rbind(chisq_a, chisq_b)
})

@@

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
mix_data_3 <- lapply(seq_along(sample_sizes), function(i) {
  n <-  sample_sizes[i]
  chisq_a <- matrix(rchisq(n*k/4, df = 3), k/4)
  chisq_b <- matrix(rchisq(n*k/4, df = 8), k/4)
  norm_a <- matrix(rnorm(n*k/4, mean = 0, sd = 1), k/4)
  norm_b <- matrix(rnorm(n*k/4, mean = 2, sd = 1.5), k/4)
  rbind(chisq_a, chisq_b, norm_a, norm_b)
})

@@

```{r fig.height=6.5, fig.width=30, dpi=300}

sample_sizes4 <- c(100, 200, 300, 400, 500)

mix_data_4 <- lapply(seq_along(sample_sizes4), function(i) {
  n <- sample_sizes4[i]
  norm_part <- matrix(rnorm(n*k/2, mean = 1, sd = 1), k/2)
  chisq_part <- matrix(rchisq(n *k /2, df =5), k /2)
  rbind(norm_part, chisq_part)
})

par(mfrow = c(1, 5))
hist(apply(mix_data_4[[1]], 1, mean))
hist(apply(mix_data_4[[2]], 1, mean))
hist(apply(mix_data_4[[3]], 1, mean))
hist(apply(mix_data_4[[4]], 1, mean))
hist(apply(mix_data_4[[5]], 1, mean))
```
